OCMu64: a solver for One-sided Crossing Minimization

### 2024-06-20 tex/description.tex
weak variatns
shrink

\begin{remark}[Tail variants]
  Our branch-and-bound method fixes vertices of the
solution from left to right. That means that at each step \cref{pg,pfp} can be applied to
just the \emph{tail}.
\end{remark}

>>>>

\begin{remark}[Weak variants]
  It is also possible to consider \emph{weak} variants of the above lemmas that
  only imply that $u<v$ or $u\g v$ in \emph{some} optimal solution. This requires careful
  handling of cycles like $u\be v\be w\be u$ and $u\g v\g w\g u$.
\end{remark}

\begin{remark}[Tail variants]
  Our branch-and-bound method fixes vertices of the
solution from left to right. Thus, at each step \cref{pg,pfp} can be applied to
just the \emph{tail}.
\end{remark}
